Metadata Repositories

### 2016-05-06 inst/examples/metadata-repositories.Rmd
update to reflect changes in dataone & datapack

```{r eval = FALSE}
install.packages("dataone", repos= c("https://cran.rstudio.com", "http://nceas.github.io/drat"))
```

```{r}
library("dataone")
library("datapackage")
```

@@

```{r}
dp <- new("DataPackage")
addData(dp, dataObj, metadataObj)
```

>>>>

```{r eval = FALSE}
#install.packages("dataone", repos= c("https://cran.rstudio.com", "http://nceas.github.io/drat"))

## or
devtools::install_github(c("ropensci/datapack", "DataONEorg/rdataone"))
```

```{r}
library("dataone")
library("datapack")
```

@@

```{r}
dp <- new("DataPackage")
dp <- addData(dp, dataObj, metadataObj)
```
